% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}
% \usepackage[russian]{babel}  % Включаем пакет для поддержки русского языка

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=OliveGreen, urlcolor=OliveGreen}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}
	
	% Name and date of last update to this document
	\noindent{\Huge{Georgiy Sapunov}
		\hfill{\it\footnotesize Updated \today}}
	
	% --- Contact information and other items ---
	
	\vspace{0.5cm}
	\begin{center}
		\begin{tabular}{lll}
			% Line 1: Email, GitHub, office location
			\textbf{Email}: GeorgiySapunov@yandex.ru      &
			%\hspace{0.55in} \textbf{GitHub}: //github-username    &
			%\hspace{0.4in} 	\textbf{Office}: Your Building 101 \\
			
			% Line 2: Phone number, LinkedIn, citizenship
			\textbf{Phone}: +7\,(952)\,391-3325
			%\hspace{0.55in} \textbf{LinkedIn}: //LinkedIn-URL   &
			\hspace{0.4in} \textbf{Citizenship}: Russia
		\end{tabular}
	\end{center}
	
	% --- Start the two-column table storing the main content ---
	
	% Set spacing between columns
	\setlength{\tabcolsep}{8pt}
	
	% Set the width of each column
	\begin{longtable}{p{1.3in}p{4.8in}}
		
		% --- Section: Research interests ---
		
		\nohyphens{\color{OliveGreen}{Research interests}}
        & Long wavelength Vertical-cavity surface-emitting laser, Molecular
        beam epitaxy, III-V semiconductors on silicon, Nanowires \\
		& \\
		
		% --- Section: Education ---
		
		\color{OliveGreen}{Education}
		& \textbf{Saint-Petersburg Academic University} \hfill Saint-Petersburg, Russia \\
		& PhD in Physics of Condensed Matter \hfill sep 2016\,--\,jul 2021 \\
        & Thesis: "Molecular Beam Epitaxy of Gallium Nitride, Gallium Arsenide,
        and Gallium Phosphide Nanostructures on Silicon" \\
		& Mentor: Bolshakov~A,\,D.\\
		& \\
		
		& \textbf{Saint-Petersburg Academic University} \hfill Saint-Petersburg, Russia \\
		& MS in Electronics and Nanoelectronics \hfill sep 2014\,--\,aug 2016\\
		& Mentor: Bolshakov~A,\,D. \\
		& \\
		
		& \textbf{Tambov State Technical University} \hfill Tambov, Russia\\
		& BS in Nanotechnology, \hfill sep 2010\,--\,aug 2014\\
		& \\
		
		% --- Uncomment the next few lines if you want to include some courses ---
		%& \textbf{Selected coursework}
		%\begin{itemize}[noitemsep,leftmargin=*]
		%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
		%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
		%\end{itemize} \\
		
		% --- Section: Awards, scholarships, etc. ---
		% --- Note: section title is spread over two lines ---
		
		{\color{OliveGreen}{Honors and scholarships}}
        & Grant for young scientists of universities and academic institutions
        located in Saint-Petersburg (Committee on Science and Higher Education)
        \hfill 2020\\
		& \\
        & Scholarship of the Government of the Russian Federation in priority
        areas of modernization and technological development of the Russian
        economy (Government of the Russian Federation) \hfill 2019\\
		& \\
        & Grant for university students located in Saint-Petersburg, graduate
        students of universities, industry and academic institutions located in
        Saint-Petersburg (Committee on Science and Higher Education)\hfill 2018
        \\
		& \\
		
		%Skills
		
		{\color{OliveGreen}{Skills}}
		& \textbf{Molecular beam epitaxy} \\
        & GaAs, GaP and GaP(NAs) planar growth, GaN, GaAs, GaP nanowire growth
        on silicon substrate using a molecular-beam epitaxy system Veeco
        GEN-III \\
		& \\
		& \textbf{Structure characterisation} \\
        & Reflection high-energy electron diffraction, Atomic Force Microscopy,
        Raman and Photoluminescence spectroscopy. \\
		& \\
        & Experience in Scanning and Transmission electron microscopy,
        Secondary ion mass spectrometry and X-ray  diffraction data
        interpretation. \\
		& \\
		& \textbf{Data analysys and visualisation} \\
        & Python (NumPy, Pandas, Scikit-learn, Keras, Tensorflow,
        Matplotlib), Machine learning, Excel, OriginLab, Gwyddion. \\
        \\
		& \textbf{Computer graphics} \\
        & Blender, Gimp, Inkscape. \\ 
		& \\
		& \textbf{Languages} \\
        & Russian (native), English (upper-intermediate), French
        (intermediate), Japanese (intermediate) \\
		& \\
		
		% --- Section: Research experience ---
		
		\nohyphens{\color{OliveGreen}{Research experience}}
        & \textbf{Saint-Petersburg Academic University, Laboratory of Renewable
        Energy Sources} \\
		& Mentor: Bolshakov~A.\,D. \hfill sep 2014\,--\,aug 2021 \\
        &
		\begin{itemize}
            \item Study of GaN nanowire formation, morphology optimisation for
                device implementation.
            \item Study of III-V nanostructure formation on silicon substrates,
                mainly GaP nanowires with GaP(NAs) heterojunctions.
            \item GaP(NAs) growth on silicon and sapphire, developing of III-V
                solar cells on silicon substrates.
            \item Design, growth and heterostructure optimization for device
                implementation, such as solar cells with carbon nanotubes as a
                top contact and flexible LED based on GaP(AsN) nanowires.
		\end{itemize}
		
		h-index: 8 \\
		& \\
		
		% --- Section: Talks and tutorials ---
		
		%{\color{OliveGreen}{Talks and tutorials}}
		%& \textbf{Title of your most recent presentation} \hfill Month Year \\
		%& Name of conference, workshop, seminar, venue, etc., or a description \\
		%& \\
		%
		%& \textbf{Title of your second most recent presentation} \hfill Month Year \\
		%& Name of conference, workshop, seminar, venue, etc., or a description \\
		%& \\
		
		% --- Section: Various skills (programming, software, languages, etc.) ---
		
		% --- Section: Publications ---
		\nohyphens{\color{OliveGreen}{Q1 Publications}}
        & \textbf{Single-Mode High-Speed 1550 nm Wafer Fused VCSELs for Narrow
        WDM Systems} \\
        & Babichev~A., Blokhin~S., Gladyshev~A., Karachinsky~L., Novikov~I.,
        Blokhin~A., Bobrov~M., Maleev~N., Andryushkin~V., Kolodeznyi~E.,
        Denisov~D., Kryzhanovskaya~N., Voropaev~K., Ustinov~V., Egorov~A.,
        Li~H., Tian~S.\,C., Han~S., Sapunov~S., Bimberg~D.
        \\
        & \textit{IEEE Photonics Technology Letters (IF: 2.486), 2023.}\\
		& \\

        & \textbf{Work function tailoring in gallium phosphide nanowires} \\
        & Sharov~V., Alekseev~P., Fedorov~V., Nestoklon~M., Ankudinov~A.,
        Kirilenko~D., Sapunov~G., Koval~O., Cirlin~G., Bolshakov~A., Mukhin~I.
        \\
        & \textit{Applied Surface Science (IF: 6.182), 2021.}\\
		& \\

        & \textbf{Tailoring Morphology and Vertical Yield of Self-Catalyzed GaP
        Nanowires on Template-Free Si Substrates} \\
        & Fedorov~V.\,V., Berdnikov~Y., Sibirev~N.\,V., Bolshakov~A.\,D.,
        Fedina~S.\,V., Sapunov~G.\,A., Dvoretckaia~L.\,N., Cirlin~G.,
        Kirilenko~D.\,A., Tchernycheva~M., Mukhin~I.\,S. \\
		& \textit{Nanomaterials (IF: 5.093), 2021.}\\
		& \\

        & \textbf{XRD Evaluation of Wurtzite Phase in MBE Grown Self-Catalyzed
        GaP Nanowires} \\
        & Koval~O.\,Y., Fedorov~V.\,V., Bolshakov~A.\,D., Eliseev~I.\,E.,
        Fedina~S.\,V., Sapunov~G.\,A., Udovenko~S.\,A., Dvoretckaia~L.\,N.,
        Kirilenko~D.\,A., Burkovsky R.G., Mukhin I.S. \\
        & \textit{Nanomaterials (IF: 5.093), 2021.}\\
		& \\

        & \textbf{Single GaN Nanowires for Extremely High Current Commutation}
        \\
        & Shugurov~K., Mozharov~A., Sapunov~G., Fedorov~V., Tchernycheva~M.,
        Mukhin~I. \\
        & \textit{Physica Status Solidi -- Rapid Research Letters (IF: 2.975), 2021.}\\
		& \\

        & \textbf{Structural and optical properties of self-catalyzed axially
        heterostructured GaPN/GaP nanowires embedded into a flexible silicone
        membrane} \\
        & Koval~O.\,Y., Fedorov~V.\,V., Bolshakov~A.\,D., Fedina~S.\,V.,
        Kochetkov~F.\,M., Neplokh~V., Sapunov~G.\,A., Dvoretckaia~L.\,N.,
        Kirilenko~D.\,A., Shtrom~I.\,V. and Islamova~R.\,M. \\
        & \textit{Nanomaterials (IF: 5.093), 2020.}\\
		& \\
		
        & \textbf{Structural and optical characterization of dilute phosphide
        planar heterostructures with high nitrogen content on silicon} \\
        & Koval~O.\,Y., Fedorov~V.\,V., Kryzhanovskaya~N.\,V., Sapunov~G.\,A.,
        Kirilenko~D.\,A., Pirogov~E.\,V., Filosofov~N.\,G., Serov~A.\,Y.,
        Shtrom~I.\,V., Bolshakov~A.\,D. and Mukhin~I.\,S. \\
        & \textit{CrystEngComm (IF: 3.269), 2020.}\\
		& \\
		
        & \textbf{Hydrogen passivation of the n-GaN nanowire/p-Si
        heterointerface} \\
        & Shugurov~K.\,Yu., Mozharov~A.\,M., Bolshakov~A.\,D., Fedorov~V.\,V.,
        Sapunov~G.\,A., Shtrom~I.\,V., Uvarov~A.\,V., Kudryashov~D.\,A.,
        Baranov~A.\,I., Mikhailovskii~V.\,Yu. and others \\
        & \textit{Nanomaterials (IF: 5.093), 2020.}\\
		& \\
		
        & \textbf{Synthesis and optical characterization of GaAs epitaxial
        nanoparticles on silicon} \\
        & Sapunov~G.\,A., Fedorov~V.\,V., Koval~O.\,Y., Sharov~V.\,A.,
        Dvoretckaia~L.\,N., Mukhin~I.\,S. and Bolshakov~A.\,D. \\
        & \textit{Crystal Growth \& Design (IF: 4.089), 2019.}\\
		& \\
		
        & \textbf{Effects of the surface preparation and buffer layer on the
        morphology, electronic and optical properties of the GaN nanowires on
        Si} \\
        & Bolshakov~A.\,D., Fedorov~V.\,V., Shugurov~K.\,Yu., Mozharov~A.\,M.,
        Sapunov~G.\,A., Shtrom~I.\,V., Mukhin M.\,S., Uvarov~A.\,V.,
        Cirlin~G.\,E. and Mukhin~I.\,S. \\
        & \textit{Nanotechnology (IF: 3.584), 2019.}\\
		& \\
		
        & \textbf{Effective suppression of antiphase domains in GaP (N)/GaP
        heterostructures on Si(001)} \\
        & Bolshakov~A.\,D., Fedorov~V.\,V., Koval~O.\,Y., Sapunov~G.\,A.,
        Sobolev~M.\,S., Pirogov~E.\,V., Kirilenko~D.\,A., Mozharov~A.\,M. and
        Mukhin~I.\,S. \\
        & \textit{Crystal Growth \& Design (IF: 4.089), 2019.}\\
		& \\
		
        & \textbf{Droplet epitaxy mediated growth of GaN nanostructures on
        Si(111) via plasma-assisted molecular beam epitaxy} \\
        & Fedorov~V.\,V., Bolshakov~A.\,D., Kirilenko~D.\,A., Mozharov~A.\,M.,
        Sitnikova~A.\,A., Sapunov~G.\,A., Dvoretckaia~L.\,N., Shtrom~I.\,V.,
        Cirlin~G.\,E. and Mukhin~I.\,S. \\
        & \textit{CrystEngComm (IF: 3.269), 2018.}\\
		& \\

        & \textbf{Dopant-stimulated growth of GaN nanotube-like nanostructures
        on Si(111) by molecular beam epitaxy} \\
        & Bolshakov~A.\,D., Mozharov~A.\,M., Sapunov~G.\,A., Shtrom~I.\,V.,
        Sibirev~N.\,V., Fedorov~V.\,V., Ubyivovk~E.\,V., Tchernycheva~M.,
        Cirlin~G.\,E. and Mukhin~I.\,S. \\
        & \textit{Beilstein journal of nanotechnology (IF: 3.114), 2018.}\\
		& \\

	    % Q2 Publications	
		\nohyphens{\color{OliveGreen}{Q2 Publications}}
        & \textbf{Theoretical modeling of the self-catalyzed nanowire growth:
        nucleation- and adsorption-limited regimes} \\
        & Bolshakov~A.\,D., Mozharov~A.\,M., Sapunov~G.\,A., Fedorov~V.\,V.,
        Dvoretckaia~L.\,N. and Mukhin~I.\,S. \\
        & \textit{Materials Research Express (IF: 1.929), 2017.}\\
		& \\

	    % Q3 Publications	
		\nohyphens{\color{OliveGreen}{Q3 Publications}}
        & \textbf{Microlens-enhanced substrate patterning and MBE growth of GaP
        nanowires} \\
        & Bolshakov~A.\,D., Dvoretckaia~L.\,N., Fedorov~V.\,V., Sapunov~G.\,A.,
        Mozharov~A.\,M., Shugurov~K.\,Yu., Shkoldin~V.\,A., Mukhin~M.\,S.,
        Cirlin~G.\,E. and Mukhin~I.\,S. \\
		& \textit{Semiconductors (IF: 0.674), 2018.}\\
		& \\

        & \textbf{Self-catalyzed MBE-grown GaP nanowires on Si(111): V/III
        ratio effects on the morphology and crystal phase switching} \\
        & Fedorov~V.\,V., Bolshakov~A.\,D., Dvoretckaia~L.\,N., Sapunov~G.\,A.,
        Kirilenko~D.\,A., Mozharov~A.\,M., Shugurov~K.\,Yu., Shkoldin~V.\,A.,
        Cirlin~G.\,E. and Mukhin~I.\,S. \\
		& \textit{Semiconductors (IF: 0.674), 2018.}\\
		& \\
		
        & \textbf{Effect of the conductive channel cut-off on operation of
        n\textsuperscript{+}--n--n\textsuperscript{+} GaN NW-based Gunn diode}
        \\
        & Mozharov~A.\,M., Vasiliev~A.\,A., Komissarenko~F.\,E.,
        Bolshakov~A.\,D., Sapunov~G.\,A., Fedorov~V.\,V., Cirlin~G.\,E. and
        Mukhin~I.\,S. \\
		& \textit{Semiconductors (IF: 0.674), 2018.}\\
		& \\

        & \textbf{Core-shell III-nitride nanowire heterostructure: negative
        differential resistance and device application potential} \\
        & Mozharov~A.\,M., Vasiliev~A.\,A., Bolshakov~A.\,D., Sapunov~G.\,A.,
        Fedorov~V.\,V., Cirlin~G.\,E. and Mukhin~I.\,S. \\
        & \textit{Semiconductors (IF: 0.674), 2018.}\\
		& \\

	    % Q4 Publications	
		\nohyphens{\color{OliveGreen}{Q4 Publications}}
        & \textbf{Two approaches to two-stage growth of GaP nanowires} \\
        & Berdnikov~Y., Fedorov~V.\,V., Sibirev~N.\,V., Bolshakov~A.\,D.,
        Fedina~S.\,V., Sapunov~G.\,A., Dvoretckaia~L.\,A., Mukhin~I.\,S. \\
        & \textit{2022 International Conference Laser Optics (ICLO), 2022.}\\
		& \\

        & \textbf{Self-consistent modeling of MBE self-catalyzed GaAs nanowire
        growth} \\
        & Fedina~S.\,V., Koryakin~A.\,A., Fedorov~V.\,V., Sapunov~G.\,A.,
        Mukhin~I.\,S. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2021.}\\
		& \\

        & \textbf{Processes of formation of epitaxial arrays of self-catalytic
        GaP nanowires on Si (111)} \\
        & Fedina~S.\,V., Fedorov~V.\,V., Berdnikov~Y.\,S., Sapunov~G.\,A.,
        Mukhin~I.\,S. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2021.}\\
		& \\
		
        & \textbf{Epitaxial synthesis of single-domain gallium phosphide on
        silicon} \\
        & Sapunov~G.\,A., Koval~O.\,Yu., Fedorov~V.\,V. and Bolshakov~A.\,D. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2020.}\\
		& \\
		
        & \textbf{Controllable antiphase domain density in dilute nitride
        GaPN/GaP heterostructures on silicon} \\
        & Fedorov~V.\,V., Bolshakov~A.\,D., Koval~O.\,Yu., Sapunov~G.\,A.,
        Sobolev~M,\,S., Pirogov~E.\,V., Kirilenko~D.\,A., Mozharov~A.\,M.,
        Mozharov~A.\,M. and Mukhin~I.\,S. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2020.}\\
		& \\
		
        & \textbf{Synthesis and characterization of GaPN/GaP heterostructures
        grown on silicon (001)} \\
        & Koval~O.\,Yu., Sapunov~G.\,A. and Fedorov~V.\,V. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2020.}\\
		& \\
		
        & \textbf{Conductive AFM study of the electronic properties of
        individual epitaxial GaN nanowires} \\
        & Sharov~V., Bolshakov~A.\,D., Fedorov~V.\,V., Shugurov~K.\,Yu.,
        Mozharov~A.\,M., Sapunov~G.\,A. and Mukhin~I.\,S. \\
		& \textit{IOP Conference Series: Materials Science and Engineering, 2019.}\\
		& \\
		
        & \textbf{Growth and optical properties of GaPN/GaP heterostructure
        nanowire array} \\
        & Koval~O.\,Yu., Sapunov~G.\,A., Fedorov~V.\,V. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2019.}\\
		& \\
		
        & \textbf{Synthesis and optical properties study of GaAs epitaxial
        nanoparticles on silicon} \\
        & Sapunov~G.\,A., Koval~O.\,Yu., Sharov~V., Dvoretckaia~L.\,N.,
        Mitin~D.\, M. and Bolshakov~A.\,D. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2019.}\\
		& \\
		
        & \textbf{GaN-nanowire/Si solar cell: numerical modeling, fabrication
        and characterization} \\
        & Shugurov~K.\,Yu., Mozharov~A.\,M., Sapunov~G.\,A., Fedorov~V.\,V.,
        Bolshakov~A.\,D., Cirlin~G.\,E. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2019.}\\
		& \\
		
        & \textbf{Influence of hydrogen plasma passivation on electrical and
        spectral characteristics of GaN nanowires/Si solar cells} \\
        & Shugurov~K.\,Yu., Mozharov~A.\,M., Fedorov~V.\,V., Bolshakov~A.\,D.,
        Sapunov~G.\,A. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2018.}\\
		& \\
		
        & \textbf{GaN nanostructures grown on Si(111) by PA-MBE via droplet
        epitaxy: SEM and HRTEM study} \\
        & Sapunov~G.\,A., Fedorov~V.\,V., Bolshakov~A.\,D., Mozharov~A.\,M.,
        Dvoretckaia~L.\,N., Kirilenko~D.\,A., Sitnikova~A.\,A. and
        Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2018.}\\
		& \\
		
        & \textbf{GaN nanowires on Si(111) substrates via molecular beam
        epitaxy: growth, electronic and optical properties} \\
        & Bolshakov~A.\,D., Fedorov~V.\,V., Sapunov~G.\,A., Mozharov~A.\,M.,
        Dvoretckaia~L.\,N., Shugurov~K.\,Yu., Shkoldin~V, Shtrom~I.\,V.,
        Mukhin~M.\,S., Cirlin~G.\,E. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2018.}\\
		& \\
		
        & \textbf{Epitaxial GaN nanotripods: morphology and crystal structure}
        \\
        & Sapunov~G.\,A., Bolshakov~A.\,D., Fedorov~V.\,V.,  Mozharov~A.\,M.,
        Kirilenko~D.\,A., Sitnikova~A.\,A. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2018.}\\
		& \\
		
        & \textbf{Influence of interface layer preparation on the electrical
        and spectral characteristics of GaN/Si solar cells} \\
        & Shugurov~K.\,Yu., Mozharov~A.\,M., Sapunov~G.\,A., Fedorov~V.\,V.,
        Bolshakov~A.\,D. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2018.}\\
		& \\
		
        & \textbf{Effect of Ga seeding layer on formation of epitaxial Y-shaped
        GaN nanoparticles on silicon} \\
        & Fedorov~V.\,V., Bolshakov~A.\,D., Mozharov~A.\,M., Sapunov~G.\,A.,
        Shtrom~I.\,V., Kirilenko~D.\,A., Sitnikova~A.\,A. and Mukhin~I.\,S. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2017.}\\
		& \\

        & \textbf{Modeling the semiconductor devices with negative differential
        resistance based on nitride nanowires} \\
        & Mozharov~A.\,M., Komissarenko~F.\,E., Bolshakov~A.\,D.,
        Fedorov~V.\,V., Sapunov~G.\,A., Cirlin~G.\,E. and Mukhin~I.\,S. \\
		& \textit{Journal of Physics: Conference Series (IF: 0.547), 2017.}\\
		& \\

        & \textbf{Synthesis of GaN nanowires on Si (111) substrates by
        molecular beam epitaxy} \\
        & Bolshakov~A.\,D., Sapunov~G.\,A., Mozharov~A.\,M., Cirlin~G.\,E.,
        Shtrom~I.\,V., Mukhin~I.\,S. \\
        & \textit{Journal of Physics: Conference Series (IF: 0.547), 2016.}\\
		& \\

		{\color{OliveGreen}{Patent}}
        & Growth of GaN nanotubes activated by doping with Si on Si substrates
        with a thin AlN buffer layer \hfill 2020\\
		
		% --- Section: Other interests/hobbies ---
		
		%\nohyphens{\color{OliveGreen}{Other interests}} & Some of your hobbies etc.\\
		
		% --- End of CV! ---
		
	\end{longtable}
\end{document}
